Sperm should evolve to make female meiosis fair.

### 2014-05-20 writeup_and_notes/male_dependent_drive.tex
rewrote caption 23, and centered figures

\begin{figure}
\includegraphics[width = 1 \textwidth]{Figures/selfprom.eps}
\caption{{\bf{A.}} A visual depiction of our model of `self-promoting' driver. 
	Transmission probabilities for alleles through female
 	 meiosis depend on sperm genotype. 
	 The non-driving $A$-allele, and self-promoting $B$-allele
	 are represented by unfilled and filled circles, respectively. 
	 {\bf{B.}} Evolution of a self-promoter and standard driver. 
	 	Assuming that the fitnesses of drive homozygotes and 
		heterozygotes are $1-s$ and $1$, respectively. 
	 	\emph{Main figure:} Boundary conditions for the invasion 
		and fixation of self-promoting and standard meiotic drivers, 
		with drive coefficient, $d$. Colored regions depict exact results, 
		while lines  represent analytical approximations. 
	 \emph{B1:}  Trajectories of sperm-dependent female drive
		 %alleles that can invade the population, 
		 each allele has $s =0.1$ against the
		 homozygotes.  The drive coefficient is denoted by color. 
 }   
\label{Eggsperm}
\end{figure}

@@

\begin{figure}
	\includegraphics[width = 0.7
          \textwidth]{Figures/twolocus.eps}
\caption{Models of a sperm-acting drive modifier tightly linked to a meiotic driver. 
{\bf (A) } Loci exist in tightly linked haplotypes (top of A). 
	Genotype of sperm at the modifier locus (ancestral and sperm acting modifier empty and filled squares, respectively) alters transmission  
	at the drive locus (circles) during female meiosis. 
	{\bf{A1)}} In the standard model of drive, 
	the driver (filled black circle) and non-driver (empty circle) are transmitted with probabilities $d_0$ 
	and $1-d_0$, respectively. 
	{\bf{A2)}} The $B^+$ haplotype increases the transmission of the drive allele ($d_1 > d_0$), and due to their shared genetic background, also increases its drive. 
	{\bf{A3 \& A4)}} The sperm-acting modifier acts to decrease drive  ($d_1=1/2$ in A3 \& A4. More generally, $d_1 < d_0$). 
		In {\bf{A3}} the drive suppressor exists on the drive background, forming the $B^-$ haplotype. 
		In {\bf{A4}} the drive suppressor exists on the non-drive background, forming the $A^-$ haplotype. 		
{\bf{(B)}} Invasion of a sperm-acting drive suppressor linked to a driver. 
	After the driver ($B$ haplotype) reaches drive selection equilibrium, we introduce a sperm acting drive modifier. 
	We assume full drive ($D_0 =1$), a recessive lethal fitness cost to drive ($h_s=0$, $s=1$) and that the sperm-acting modifier results in a fair meiosis. 
{\bf {B1)}} The $B^-$ allele replaces the ancestral drive haplotype, but segregates at a lower equilibrium frequency.
{\bf {B2)}} The $A^-$ allele replaces the ancestral non-driving haplotype, and in this case, removes the driver from the population. }
 \label{Eggsperm_3_allele_cartoon}
\end{figure}

>>>>

\begin{figure}
\begin{center}
\includegraphics[width = 1 \textwidth]{Figures/selfprom.eps} \end{center}
\caption{{\bf{A.}} A visual depiction of our model of `self-promoting' driver. 
	Transmission probabilities for alleles through female
 	 meiosis depend on sperm genotype. 
	 The non-driving $A$-allele, and self-promoting $B$-allele
	 are represented by unfilled and filled circles, respectively. 
	 {\bf{B.}} Evolution of a self-promoter and standard driver. 
	 	Assuming that the fitnesses of drive homozygotes and 
		heterozygotes are $1-s$ and $1$, respectively. 
	 	\emph{Main figure:} Boundary conditions for the invasion 
		and fixation of self-promoting and standard meiotic drivers, 
		with drive coefficient, $d$. Colored regions depict exact results, 
		while lines  represent analytical approximations. 
	 \emph{B1:}  Trajectories of sperm-dependent female drive
		 %alleles that can invade the population, 
		 each allele has $s =0.1$ against the
		 homozygotes.  The drive coefficient is denoted by color. 
 }   
\label{Eggsperm}
\end{figure}

@@

\begin{figure}
\begin{center}
	\includegraphics[width = 0.7
          \textwidth]{Figures/twolocus.eps} \end{center}
\caption{Models of a sperm-acting drive modifier tightly linked to a meiotic driver. 
{\bf (A) } 
Sperm carrying the derived allele at the modifier locus (filled squares) alters transmission  
	at the driving allele (filled circles) during female meiosis.
        Alleles at these two tightly linked loci form three haplotypes (top of A). 	
	{\bf{A1)}} In the standard model of drive there is no
        variation at the modifier, 
	and the driver is transmitted to the egg with probability $d_0$ 
	{\bf{A2)}} The modifier allele increases the transmission of the drive allele ($d_1 > d_0$), and due to their shared genetic background, also increases its drive. 
	{\bf{A3 \& A4)}} The sperm-acting modifier acts to decrease
        drive  ($d_1=1/2$ or more generally, $d_1 < d_0$) and arises on the same or opposite
        background from the driver (A3 \& A4 respectively). 
%		In {\bf{A3}} the drive suppressor exists on the drive background, forming the $B^-$ haplotype. 
%		In {\bf{A4}} the drive suppressor exists on the non-drive background, forming the $A^-$ haplotype. 		
{\bf{(B)}} Invasion of a sperm-acting drive suppressor linked to a driver. 
	After the driver ($B$ haplotype) reaches drive selection equilibrium, we introduce a sperm acting drive modifier. 
	We assume full drive ($D_0 =1$), a recessive lethal fitness cost to drive ($h_s=0$, $s=1$) and that the sperm-acting modifier results in a fair meiosis. 
{\bf {B1)}} The $B^-$ allele replaces the ancestral drive haplotype, but segregates at a lower equilibrium frequency.
{\bf {B2)}} The $A^-$ allele replaces the ancestral non-driving haplotype, and in this case, removes the driver from the population. }
 \label{Eggsperm_3_allele_cartoon}
\end{figure}
